# SARAR regression

Load the data. Note that numeric predictor variables have been log-transformed. For data description (including data collection, filtering, and merging), please see [the paper](https://www.sciencedirect.com/science/article/pii/S1618866720306117).

```{r}
library(spdep)
library(sp)
library(maptools)
library(rgdal)

load("data/df_merged_filtered_logged.RData")
```

Load the spatial data.

```{r}
# read shapefile of Zillow neighborhoods
zillow_poly <- readShapePoly('data/Zillow_All_States.shp')

# make the RegionID numeric
zillow_poly$RegionID <- as.numeric(as.character(zillow_poly$RegionID))

# drop some columns that we don't need
drops <- c("fid","State", "County", "City", "Name", "layer", "path", "population") 
zillow_poly <- zillow_poly[,!(names(zillow_poly) %in% drops)] 

# remove duplicate regionIDs
df <- df[!duplicated(df[ , c("RegionID")]),]

# merge the spatial data to the non-spatial data
df_spatial <- sp::merge(zillow_poly, df, by="RegionID", duplicateGeoms=T)

# get rid of extra regions
df_spatial <- df_spatial[df_spatial$RegionID %in% df$RegionID,]
```

To save computation time, subset the city of Charlotte, North Carolina. 

```{r}
# North Carolina only
df_nc <- df_spatial[df_spatial@data$State %in% c("NC"),]

# Charlotte only
df_charlotte <- df_nc[df_nc@data$CountyName %in% c("Mecklenburg County"),]
```

Plot the ZHVI for Mecklenburg County. This is the median home price per square foot. 

```{r}
spplot(df_charlotte, "price", main = "", sub = "ZHVI", col = "black")
```

Spatial autoregression models account for the influence of adjacent observations. Therefore, we need to know which observations (Zillow neighborhoods) are next to which. The weights matrix $W$ tells us which observations are adjacent. 

```{r}
# calculate weights matrix
list.queen<-poly2nb(df_charlotte, queen=TRUE) # options are queen or rook

# convert to list
W<-nb2listw(list.queen, style="W", zero.policy=T)
```

Before we continue, let's check for spatial autocorrelation in the first place. If there is no spatial autocorrelation, then there is no point in making a spatial autoregressive model!

```{r}
# Linear model without spatial autocorrelation
mod_linear <- lm(log(price) ~ 
            median_number_rooms
           + popden
           + park
           + tcc
           + ndvi
           + open_space_fraction,
           data = df_charlotte@data)
summary(mod_linear)
```

Check for spatial autocorrelation using Moran's I test. 

```{r}
# moran's test
moran.lm <- lm.morantest(mod_linear, W, alternative="two.sided", zero.policy = T)
print(moran.lm)
```

Moran tells us that the data *are* spatially autocorrelated. So, let's make a spatial autoregressive model. 

We will incorporate the weights matrix $W$ to create a spatial autoregressive model. 

```{r}
mod_spatial <- sacsarlm(log(price) ~ 
            median_number_rooms
           + popden
           + park
           + tcc
           + ndvi
           + open_space_fraction,
           data = df_charlotte,
           listw = W,
           zero.policy = T)
summary(mod_spatial, Nagelkerke=T)
```

It is important to remember that coefficients of spatial autoregressive models are interpreted differently than those of linear models. We must consider the direct, indirect, and total effects of each variable (see paper for explanation). 

```{r}
# calculate the direct, indirect, and total effects
summary(impacts(mod_spatial, listw = W, R=2000), zstats=TRUE, short=TRUE)
```


